Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-10 ms.tex
intro sentences for conclusion discussion of emission model comparisons

\subsection{Single-MBB versus Two-component emission}
% could use an opening sentence here just reiterating that a major thrust of
% this work was to decide whether the two-component model
% still makes sense after swapping in Planck for FIRAS

% second sentence of opening paragraph reiterating what the basic two
% strategies were that we employed to compare dust SED models

@@

@@

>>>>

\subsection{Single-MBB versus Two-component emission}
A major aim of this work has been to determine whether the  FDS99 
two-component dust emission model (or an FDS99-like model) remains favored over
single-MBB models when swapping the \PLANCK~HFI maps for FIRAS at frequencies 
below 1250 GHz. We compared dust SED models in two ways (1) by fitting a 
100-3000 GHz spectrum composed of per-band correlation slopes versus 
\PLANCK~857 GHz (2) by finding the best-fit dust temperature and optical depth
per line-of-sight, with each pixel's SED comprised of 100-3000 GHz 
\PLANCK+DIRBE data, and comparing the average goodness-of-fit under various
emission models.

@@

% one or two last sentence(s) saying two-component model still alive, wasn't
% an artifact of FIRAS, and also the predictions from our data release
% are a suitable alternative for estimating CMB foregrounds and can provide
% a handle on foreground systematics when swapped for other

% nevertheless, ...
% in above paragraph, say which single-MBB beta(s) we find to be favored

@@

% should there be a future work section or can the suggestions/plans of
% future work just be a part of ``SFD replacement'' subsection
